---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  dpi = 300
)
```

# cccLLM

<!-- badges: start -->

[![R-CMD-check](https://github.com/acastroaraujo/cccLLM/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/acastroaraujo/cccLLM/actions/workflows/R-CMD-check.yaml)

<!-- badges: end -->

This package contains a collection of datasets about the Colombian Constitutional Court collected with the help of Large Language Models. It is meant to complement the datasets collected in the [ccc](https://acastroaraujo.github.io/ccc/) package.

## Installation

You can install the development version of cccLLM from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("acastroaraujo/cccLLM")
```

A BibTeX entry for LaTeX users is:

```{r, comment="", echo=FALSE}
toBibtex(citation("cccLLM"))
```

## Overview

-   `rulings`

-   `person`

-   `amicus`

-   `articles`

-   `rj_citations`

-   `appointed_judges`

## 

```{r court-cohorts, message=FALSE, fig.height = 6, fig.width = 7, echo=FALSE}
library(tidyverse)
library(cccLLM)

theme_set(theme_light(base_family = "Avenir Next Condensed"))

lvls <- with(appointed_judges, str_to_title(name[order(start, end)]))

appointed_judges |>
  mutate(name = str_to_title(name)) |> 
  mutate(name = factor(name, lvls)) |>
  ggplot(aes(y = name)) +
  geom_segment(aes(x = start, xend = end)) +
  labs(
    x = NULL, y = NULL, 
    title = "The Colombian Constitutional Court",
    subtitle = "1992-2024"
    ) + 
  scale_x_date(date_breaks = "2 years", date_labels = "'%y")
```
