---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# cccLLM

<!-- badges: start -->

<!-- badges: end -->

This repository contains code to extract information from court rulings using LLMs via the new [ellmer](https://ellmer.tidyverse.org/) package.

For using LLMs like ChatGPT you will have to add something like this to your `.Renviron` file:

```         
OPENAI_API_KEY = "you_api_goes_here"
```

If you don't know where this file is located, you can use the following function:

```         
usethis::edit_r_environ(scope = "user")
```

## Structured Output

The JSON schema I used was constructed using the ellmer package in R.

See [here](https://acastroaraujo.github.io/blog/posts/2025-03-17-llms-for-researchers/#structured-output) for more information on the "structured output" capabilities of some LLMs.

You can find both the system prompt and JSON schema in the `prompts` directory.

```{r}
source("prompts/ruling_summary.R")
ruling_summary
```

## Example

```{r}
out <- readRDS("out_raw/C-1060A-01_gpt.rds")
out
```

## Manual Coding of Very Large Files

Some documents exceed the maximum context length of 128000 tokens. This happens, for example, when a lengthy appendix is included in the file. This means I couldn't parse them in the same ways as the others.

These documents were manually coded, with the exception of the English and Spanish summaries which were written using the file upload option in the OpenAI platform.

They can be found in the `out_raw_exceeded` directory.

*Working with the document embeddings provided by OpenAI's RAG system produce very unreliable results.* There is a higher chance that the somes fields here — e.g., `articles` and `amicus` — are miscoded. I've tried my best to keep things reliable via manual inspection! This is why there is a `model` variable in the codebook that distinguishes between "gpt-4o" and "acastroaraujo".

I recommend you double-check these rulings if you are going to analyze the `articles` variable.

## Codebook

1.  `id`: Ruling ID.

    Each ruling has a standardized name. The infix carries no meaning; the suffix indicates the year in which the ruling was made; and the prefix refers to the type of ruling.

    Type of ruling:

    -   `C`. Refers to *sentencia de constitucionalidad,* or the cases in which the CCC decides whether a law, rule, or administrative decision is compatible with constitutional norms.

    -   `T`. Refers to *tutela*, which is an individual complaint mechanism aimed at the protection of fundamental rights (or special protection writ).

    -   `SU`. Refers *sentencia de unificación,* or decisions in which the Court has decided to compile and standardize the decisions made in various `T` rulings.

    [For example: *T-406-92, SU-039-97, C-225-1995, C-776-03, T-025-04, SU-1184-01*]{style="font-size: 0.8em;"}

2.  `url`: Document address in CCC website.

    [*For example: <https://www.corteconstitucional.gov.co/relatoria/1994/c-221-94.htm>*]{style="font-size: 0.8em;"}

3.  `chamber_raw`: Refers to the parsed non-standardized name of the chamber that authored the ruling.

    [For example: *Sala Séptima de Revisión de Tutelas*, *Sala Plena de Conjueces*]{style="font-size: 0.8em;"}

4.  `chamber`: Refers to the kind of chamber that authored the ruling, which can be either a three-person chamber (`SR`, *sala de revisión)* or a full-chamber (`SP`, *sala plena).*

5.  `person`:

    -   `name`: Name of judge.

    -   `mp`: Authoring judge *(magistrado ponente).*

    -   `sv`: Dissenting opinion *(salvamento de voto).*

    -   `av`: Concurring opinion *(aclaración de voto).*

    -   `conjuez`: Whether the judge is holds a permanent position in the court or was appointed for this specific ruling. This happens, for example, when one of the judges in the CCC recuses themselves.

    *Note. Most of the time this is a three row data frame in case the chamber composed of a three-person chamber (`SR`) or a nine row data frame in case of full-chamber (`SP`).*

    For example:

    | name                        | av      | sv      | mp      | conjuez |
    |-----------------------------|---------|---------|---------|---------|
    | `Vladimiro Naranjo Mesa`    | `FALSE` | `FALSE` | `TRUE`  | `FALSE` |
    | `Antonio Barrera Carbonell` | `FALSE` | `FALSE` | `FALSE` | `FALSE` |
    | `Alfredo Beltrán Sierra`    | `FALSE` | `FALSE` | `FALSE` | `FALSE` |

6.  `articles`: List of articles of the Constitution that are object of discussion.

    [For example: *23, 212, 213, 215*]{style="font-size: 0.8em;"}

7.  `summary_en`: Two paragraph summary in English.

8.  `summary_es`: Two paragraph summary in Spanish.

9.  `rj`: Refers to *res judicata (cosa juzgada)* and notes whether the court's decision is determined by previous binding rulings or not. This meant to prevent the same constitutional issue from being raised again in future cases.

10. `rj_citation_raw` (only if `rj` is `TRUE`): List of rulings cited as binding.

    [For example: *Sentencia T-406 de 1992, Sentencia C-225/95*]{style="font-size: 0.8em;"}

11. `rj_citation:` Standardized list of rulings cited as binding.

    [For example: *T-406-92, C-225-95*]{style="font-size: 0.8em;"}

## Misc.

The `amicus` field contains information about participants acting as amicus curiae ("friends of the court") in the corresponding ruling. The output may include individual people, NGOs, professional associations, labor unions, universities, government entities, and other types of public or private organizations.

There is one inconsistency in how the Office of The Inspector General ("Procuraduría General de La Nación") is coded in this field. Since it is mandatory for each `C` ruling to contain the input of this office (see article 242 of the Colombian Constitution), this intervention is sometimes separated from the interventions of other third parties. Thus, this government agency shows up in the `amicus` field in an inconsistent fashion. The best way to treat this issue is to remove this office from all `amicus` fields in all `C` rulings.
