---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# cccLLM

<!-- badges: start -->

<!-- badges: end -->

This repository contains code to extract information from court rulings using LLMs via the new [ellmer](https://ellmer.tidyverse.org/) package.

For using LLMs like ChatGPT you will have to add something like this to your `.Renviron` file:

```         
OPENAI_API_KEY = "you_api_goes_here"
```

If you don't know where this file is located, you can use the following function:

```         
usethis::edit_r_environ(scope = "user")
```

## Structured Output

The JSON schema I used was constructed using the ellmer package in R.

See [here](https://acastroaraujo.github.io/blog/posts/2025-03-17-llms-for-researchers/#structured-output) for more information on the "structured output" capabilities of some LLMs.

You can find both the system prompt and JSON schema in the `prompts` directory.

```{r}
source("prompts/ruling_summary.R")
ruling_summary
```

## Example

```{r}
out <- readRDS("out_raw/C-1060A-01_gpt.rds")
out
```

## Manual Coding of Very Large Files

Some documents exceed the maximum context length of 128000 tokens. This means I couldn't parse them in the same ways as the others.

These documents were manually coded, with the exception of the English and Spanish summaries which were written using the file upload option in the OpenAI platform.

They can be found in the `out_raw_exceeded` directory.

```{r}
length(dir("out_raw_exceeded"))
```

There is a higher chance that the somes fields here — e.g., `articles` and `amicus` — are miscoded.

*In sum, working with the document embeddings provided by OpenAI's RAG system produce very unreliable results.*

## Codebook

1.  `id`: Ruling ID.

    Each ruling has a standardized name. The infix carries no meaning; the suffix indicates the year in which the ruling was made; and the prefix refers to the type of ruling.

    Type of ruling:

    -   `C`. Refers to *sentencia de constitucionalidad,* or the cases in which the CCC decides whether a law, rule, or administrative decision is compatible with constitutional norms.

    -   `T`. Refers to *tutela*, which is an individual complaint mechanism aimed at the protection of fundamental rights (or special protection writ).

    -   `SU`. Refers *sentencia de unificación,* or decisions in which the Court has decided to compile and standardize the decisions made in various `T` rulings.

    [For example: *T-406-92, SU-039-97, C-225-1995, C-776-03, T-025-04, SU-1184-01*]{style="font-size: 0.8em;"}

2.  `url`: Document address in CCC website.

    [*For example: <https://www.corteconstitucional.gov.co/relatoria/1994/c-221-94.htm>*]{style="font-size: 0.8em;"}

3.  `chamber_raw`: Refers to the parsed non-standardized name of the chamber that authored the ruling.

    [For example: *Sala Séptima de Revisión de Tutelas*, *Sala Plena de Conjueces*]{style="font-size: 0.8em;"}

4.  `chamber`: Refers to the kind of chamber that authored the ruling, which can be either a three-person chamber (`SR`, *sala de revisión)* or a full-chamber (`SP`, *sala plena).*

5.  `person`:

    -   `name`: Name of judge.

    -   `mp`: Authoring judge *(magistrado ponente).*

    -   `sv`: Dissenting opinion *(salvamento de voto).*

    -   `av`: Concurring opinion *(aclaración de voto).*

    -   `conjuez`: Whether the judge is holds a permanent position in the court or was appointed for this specific ruling. This happens, for example, when one of the judges in the CCC recuses themselves.

    *Note. Most of the time this is a three row data frame in case the chamber composed of a three-person chamber (`SR`) or a nine row data frame in case of full-chamber (`SP`).*

    For example:

    | name                        | av      | sv      | mp      | conjuez |
    |-----------------------------|---------|---------|---------|---------|
    | `Vladimiro Naranjo Mesa`    | `FALSE` | `FALSE` | `TRUE`  | `FALSE` |
    | `Antonio Barrera Carbonell` | `FALSE` | `FALSE` | `FALSE` | `FALSE` |
    | `Alfredo Beltrán Sierra`    | `FALSE` | `FALSE` | `FALSE` | `FALSE` |

6.  `articles`: List of articles of the Constitution that are object of discussion.

    [For example: *23, 212, 213, 215*]{style="font-size: 0.8em;"}

7.  `summary_en`: Two paragraph summary in English.

8.  `summary_es`: Two paragraph summary in Spanish.

9.  `rj`: Refers to *res judicata (cosa juzgada)* and notes whether the court's decision is determined by previous binding rulings or not. This meant to prevent the same constitutional issue from being raised again in future cases.

10. `rj_citation_raw` (only if `rj` is `TRUE`): List of rulings cited as binding.

    [For example: *Sentencia T-406 de 1992, Sentencia C-225/95*]{style="font-size: 0.8em;"}

11. `rj_citation:` Standardized list of rulings cited as binding.

    [For example: *T-406-92, C-225-95*]{style="font-size: 0.8em;"}
